External validation

### 2021-02-05 diagnostics/README.Rmd
Updated report

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
#  github_document:
#    toc: yes
#    df_print: "kable"
  html_document:
    toc: yes
    df_print: "kable"
    toc_float: yes
    number_sections: yes
    code_folding: "hide"
    keep_md: yes
bibliography: 
  # C:\\Users\\erik_\\Documents\\library.bib
  H:\\zotero_lib.bib
---

@@

Load the exported models to validate (also found "manually" at [Github](https://github.com/eribul/NH_luxation_infektion/blob/master/cache/ext_val_required_data.RData)). This is a nested data frame with one row for each prediction period (90 days and 2 years). Column `fit` contains `glm` objects stripped from any personal patient data.

```{r}
# Load the exported model object
load("../cache/fit_brl_reduced_lean.RData")
```

Let's inspect the model for 90 days just to get a sence of it:

```{r}
fit_brl_reduced_lean$fit[[1]]
```

@@

The outcome variables are simply called `outcome` in each model (hence, adjusted for each model). Those are logical/boolean (or 0/1-numeric) indicating whether the patient got PJI within 90 days (2 years) after THA (`TRUE`/1) or not (`FALSE`/0). Note that we had previously excluded all patients who died within two years. A competing risk model for survival analysis might be better but we were pragmatic in this case.

We identified PJI within 90 days/2 years as either the primary or secondary reson for reoperation performed within this time frame, as recorded to SHAR, or if a relevant ICD-10/NOMESCO code was recorded during a hospitl visit/admission during this period.

@@

... are logical/boolean indicators of comorbidities based on ICD-10/ATC codes from one year prior to THA, as recorded in our National Patient Register and medical prescription register. Individual codes were grouped according to Charlson and Elixhauser as codified by table 2 in \@Quan2005, and as RxRisk V according to table 1 in \@Pratt2018. Those conditions were then further combined according to table 1 in the drafted manuscript:

@@

```{r}
model <- fit_brl_reduced_lean$fit[[1]]
```

@@

```{r}
outcome <- df$outcome_infection_90d
X       <- ext_val_required_data
```

@@

# 2 years

Repeat for the 2-year model.

>>>>

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
#  github_document:
#    toc: yes
#    df_print: "kable"
  html_document:
    toc: yes
    df_print: "kable"
    toc_float: yes
    number_sections: yes
    code_folding: "hide"
    keep_md: yes
bibliography: 
  C:\\Users\\erik_\\Documents\\library.bib
  # H:\\zotero_lib.bib
---

@@

Load the exported models to validate (also found "manually" at [Github](https://github.com/eribul/NH_luxation_infektion/blob/master/cache/ext_val_required_data.RData)).

```{r}
# Load the exported model object
load("../cache/model_reduced_lean.RData")
```

Let's inspect the model for 90 days just to get a sense of it:

```{r}
model_reduced_lean
```

@@

The outcome variable is simply called `outcome` . This is a logical/boolean (or 0/1-numeric) variable indicating whether the patient got PJI within 90 days after THA (`TRUE`/1) or not (`FALSE`/0).

We identified PJI within 90 days as either the primary or secondary reason for reoperation performed within this time frame, as recorded to SHAR, or if a relevant ICD-10/NOMESCO code was recorded during a hospital visit/admission during this period.

@@

... are logical/boolean indicators of comorbidities based on ICD-10 codes from one year prior to THA, as recorded in our National Patient Register. Individual codes were grouped according to Charlson and Elixhauser as codified by table 2 in \@Quan2005. Those conditions were then further combined according to table 1 in the drafted manuscript:

@@

```{r}
model <- model_reduced_lean
```

@@

```{r}
outcome <- df$outcome
X       <- ext_val_required_data
```

@@
